### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	15:55:51	(Tue18.Mar)
la2pdf commit - 2014:03:18	15:58:41	(Tue18.Mar)

\ai{It is indeed. We dedicated the second paragraph in the discussion (IV) to this topic, but will reword the relevant result paragraph slightly to hopefully cause less confusion.}

@@

\ai{We agree that this should hould be clarified, and have We disagree that this }

>>>>

\ai{It is indeed. We dedicated the second paragraph in the discussion (IV) to this topic, but have revised the paragraph to emphasize this point better.}

@@

\ai{We agree that this should should be clarified, and }
